---
title: "Lab 1: Introduction to Quarto"
author: "Agustin Fleisher"
date: "September 22, 2025"
editor: source
embed-resources: true
execute:
  echo: true
  error: true
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
    theme: litera
---

# Exploring Quarto Documents

## Specifying Global Execute Options

Execution options specify how the R code in your Quarto document should be
displayed. This [guide](https://quarto.org/docs/computations/execution-options.html)
provides descriptions on the options you can specify in a document's execution.

**Question 1** -- Add your name and the date to the YAML. 

**Question 2** -- Add an `execute` line to your YAML that includes the following
options, (1) your source code is always output on the page, and (2) your
document will render even if there are errors.

## Tooth Growth Dataset

```{r}
#| echo: true
#| label: practicing-running-code

# Load a dataset into the R Environment.
data(ToothGrowth)

# Look at the summary of the variables in the dataset.
summary(ToothGrowth)
```

**Question 3** -- Let's spice this code up a bit. Delete `1 + 1` from the code
chunk and paste in the code provided in the Lab 1 instructions. 

## Check the Data Documentation

**Question 4** -- In your **console** (*not* in the Quarto document), type
`?ToothGrowth` (or alternatively `help(ToothGrowth)`. Use the information that
pops up in the *Help* pane in RStudio to fill in the blanks below. 

*This dataset investigates the effect of **Vitamin C** on tooth growth in **guinea pigs**.*

*The two supplement delivery methods include **OJ (orange juice)** and **VC (ascorbic acid)**.*

*`ToothGrowth` is a data frame with **60 observations** and **3 variables**.*

**Question 5** -- *Before* the code chunk, change the "Running the Provided
Code" section header to a header that better describes the contents of this
section (e.g., Tooth Growth Dataset).

## Creating a Plot

**Question 6** -- Replace the `plot(pressure)` code with the code provided in the Lab 1 instructions.

```{r}
#| echo: true
#| label: creating-a-plot
#| layout-ncol: 2
#| fig-align: center
#| fig-cap: ["OJ group shows slightly higher tooth lengths on average",
#|            "Higher supplement doses lead to greater tooth growth"]
library(tidyverse)

ggplot(data = ToothGrowth, 
       mapping = aes(x = supp, y = len)) +
  geom_boxplot() +
  labs(x = "Supplement", y = "Length of Teeth (mm)")

ToothGrowth %>% 
  mutate(dose = as.factor(dose)) %>% 
  ggplot(mapping = aes(x = dose, y = len)) +
  geom_boxplot() +
  labs(x = "Dose of Supplement (mg/day)", y = "Length of Teeth (mm)")
```

Now, run this code chunk! You should see two side-by-side boxplots, one plot
comparing tooth length between the two supplement delivery methods and one plot
comparing tooth length between the three different dosages uses. 

**Question 7** -- Read over the [Quarto documentation on figure options](https://quarto.org/docs/authoring/figures.html#computations)
and add an option (`#|`) to the above code chunk to make the figures print
side-by-side (i.e., in one row) in the rendered HTML file. 

**Question 8** -- Specify in the code chunk options that these boxplots 
should be **center aligned** (also found in the Quarto documentation).

**Question 9** -- Specify a **figure caption** for the boxplots (using a
code-chunk option). This is a bit tricky! There are two plots, so you will need
to figure out how to specify a different caption for each plot. 
```{r}
t.test(len ~ supp, data = ToothGrowth, var.equal = FALSE)
```
1. Conclusion: The p-value from Welch’s two-sample t-test was 0.06063 (> 0.05). We fail to reject the null hypothesis. In these data, there isn’t strong evidence that the mean tooth length differs between the OJ and VC methods.

2. Confidence interval: Using the default 95% confidence level, the CI for the difference in means (OJ − VC) is [−0.171, 7.571] mm. Because this interval includes 0, the true difference could be zero. This is consistent with the sample means (OJ = 20.663, VC = 16.963), which suggest OJ tends to be higher on average but not significantly so at α = 0.05. (I had to get help for this one)

## Interpretation of the Two-Sample t-Test